Fusion Moves for Correlation Clustering

### 2014-11-07 paper/anytimefigure2.tex
fiure update

  \anytimeplot{socialnets} 

@@

  \anytimeplot{normalizedsocialnets}

>>>>

  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/socialnets.data};              \addlegendentry{HC}
  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/socialnets.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/socialnets.data};               \addlegendentry{CGC}
  %\addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/normalizedsocialnets.data};          \addlegendentry{KL}
  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/socialnets.data};     \addlegendentry{MC-R}
  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/socialnets.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/socialnets.data};    \addlegendentry{Fusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/socialnets.data};    \addlegendentry{Fusion-HC-CGC}
  %\addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-MC}
  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/socialnets.data};  \addlegendentry{Fusion-WS-CGC}
  %\anytimeplot{socialnets} 

@@

  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/normalizedsocialnets.data};              \addlegendentry{HC}
  %\addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/normalizedsocialnets.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/normalizedsocialnets.data};               \addlegendentry{CGC}
  %\addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/normalizedsocialnets.data};          \addlegendentry{KL}
  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/normalizedsocialnets.data};     \addlegendentry{MC-R}
  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/normalizedsocialnets.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/normalizedsocialnets.data};    \addlegendentry{Fusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/normalizedsocialnets.data};    \addlegendentry{Fusion-HC-CGC}
  %\addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-MC}
  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-CGC}
 % \anytimeplot{normalizedsocialnets}
